Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2015-06-02 tese/state03.tex
end of SotA 3, gonna sleep

@@

  Using technologies that relies only on web standards, like \ac{CSS}, \ac{HTML}5, \emph{JavaScript} and \ac{SVG}, will make possible to develop an application that solves our problem with the advantage of being compatible with a greater amount of web browsers.
  %RP não concordo com frase. O que o uso de tecnologias standard faz é garantir que a app é suportada em vários dispositivos. Também podes dizer as essas tecnologias já permitem desenvolver a applicação que tens em mente, mas isso é outra coisa.
  %RP evita ser tão ``vendedor''. Não digas coisas como ``to a new level'' mas cinge-te a afirmaçãos objectivas.
  For example, with \ac{API}s like WebGL\footnote{\url{http://khronos.org/webgl/}}, it is now possible to manipulate a three dimensional environment in the context of a hyper-call. Another example would be a collaborative spreadsheet using \ac{WebRTC}. With this, hyper-calls are not limited to only audio, image, text and video, but also interaction with complex graphical user interfaces that changes over time.
 %XXX
  %RP porque escolheste falar aogra de webgl se não falas antes?

  In this project our goal is to enrich hyper-calls with no limits, every user should be free to choose how it wants to be contacted and how he wants to share its contents.
  %RP O ``no limits'' é muito vago. Tens de ser mais objectivo.

  In order to give users a personalized communication channel, each user must have a personal web page where its available plug-ins could be downloaded from other peers, after that, they can talk in the same language whatever it is.
%RP acho que aqui já estás a falar de detalhes de implementação que o leitor não tem possibilidade de perceber antes de descreveres as funcionalidades de aplicação e a sua arquitectura.

>>>>

  For example, with \ac{API}s like WebGL\footnote{\url{http://khronos.org/webgl/}}, it is now possible to manipulate a three dimensional environment in the context of a hyper-call. Another example would be a collaborative spreadsheet using \ac{WebRTC}. With this, hyper-calls are not limited to only audio, image, text and video, but also interaction with complex graphical user interfaces that changes over time.
 %XXX
  %RP porque escolheste falar aogra de webgl se não falas antes?
%HR já troquei, o WebGL usa o canvas do HTML5, talvez seja este o local mais adequado

@@

  Using technologies that relies only on web standards, like \ac{CSS}, \ac{HTML}5, \emph{JavaScript} and \ac{SVG}, will make possible to develop an application that solves our problem with the advantage of being compatible with a greater amount of web browsers.
  %RP não concordo com frase. O que o uso de tecnologias standard faz é garantir que a app é suportada em vários dispositivos. Também podes dizer as essas tecnologias já permitem desenvolver a applicação que tens em mente, mas isso é outra coisa.
  %RP evita ser tão ``vendedor''. Não digas coisas como ``to a new level'' mas cinge-te a afirmaçãos objectivas.

  %In this project our goal is to enrich hyper-calls with no limits, every user should be free to choose how it wants to be contacted and how he wants to share its contents.
  %RP O ``no limits'' é muito vago. Tens de ser mais objectivo.
  %HR tanto esta como a seguinte frase foram escritas praticamente no inicio do estado de arte, nem faz sentido estarem aqui.

  %In order to give users a personalized communication channel, each user must have a personal web page where its available plug-ins could be downloaded from other peers, after that, they can talk in the same language whatever it is.
%RP acho que aqui já estás a falar de detalhes de implementação que o leitor não tem possibilidade de perceber antes de descreveres as funcionalidades de aplicação e a sua arquitectura.
